### 2023-10-30 README.Rmd
updatEs

4. Running mega detector on images using the bash script.

```{bash eval=FALSE}
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/my_passport_images" \ 
  -m "/workspace/models/md_v5a.0.0.pt" \
  md
```

@@

>>>>

4. Activate ENV, then run mega detector on images using the bash script.

```{bash eval=FALSE}
mamba activate cameratraps-detector
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/my_passport_images" \ 
  -m "/workspace/models/md_v5a.0.0.pt" \
  md
```

@@

7. Optionally, write out the visualizations of the detections.

```{bash eval=FALSE}
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/my_passport_images" \
  -i "/workspace/rofcamtrap/1_MegaDetector/1_outputs_no_repeats/" \
  -o "/workspace/rofcamtrap/1_MegaDetector/2_visualize/" \
  viz
```

8. Convert to coco and ls [and 3rd format?].

```{bash eval=FALSE}
mamba deactivate 
cd mdtools
poetry shell
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/my_passport_images" \
  -i "/workspace/rofcamtrap/1_MegaDetector/1_outputs_no_repeats/" \
  -o "/workspace/rofcamtrap/2_LabelStudio/0_inputs/" \
  repeat-convert
```
